Visualizations for the manuscript

### 2022-03-22 metanalysis_visualization/manuscript_Figures.Rmd
update supplementary figure 2 as a heatmap

```{r libraries, message=FALSE, warning=FALSE, results='hide'}
# Install packages
paket <- function(pak){
  new_pak <- pak[!(pak %in% rownames(installed.packages()))]
  if (length(new_pak)) 
    install.packages(new_pak, dependencies = TRUE,repos="https://cloud.r-project.org/")
  sapply(pak, library, character.only = TRUE)
}
listOfPackages <- c("tidyverse", "tidyr","devtools","RColorBrewer", "knitr", "kableExtra", "tsModel", "gridExtra", "dplyr", "metafor", "meta", "viridis", "UpSetR", "scales")
paket(listOfPackages)

@@

perc_disorder_group_total %>%
  ggplot( aes( x= as.Date( time_p ), y = percentage, group = disorder_group )) +
  geom_line( aes(color = disorder_group )) +
  geom_point( aes( color = disorder_group )) +
  geom_vline(xintercept = as.Date(pandemic_start_date), linetype = "dashed")+
  labs(x ="", y = "percentage of patients (%)")+
  scale_x_date(breaks = "1 month", labels=date_format("%b-%y"), expand=c(0.03,0))+
  theme(axis.text.x=element_text(angle = 45, hjust=1, size = 6),
        panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        panel.border = element_rect(colour = "black", fill = NA))
#   
# perc_disorder_group_country <- perc_disorder_group_all %>%
#   select( - percentage_dg ) %>%
#   inner_join( country_map ) %>%
#   group_by( time_p, disorder_group, country ) %>%
#   mutate( total_cases = sum( count_icd ), 
#           dg_cases = sum( count_dg ), 
#           percentage = 100* dg_cases / total_cases ) %>%
#   rbind( perc_disorder_group_total)

>>>>

```{r libraries, message=FALSE, warning=FALSE, results='hide'}
# Install packages
paket <- function(pak){
  new_pak <- pak[!(pak %in% rownames(installed.packages()))]
  if (length(new_pak)) 
    install.packages(new_pak, dependencies = TRUE,repos="https://cloud.r-project.org/")
  sapply(pak, library, character.only = TRUE)
}
listOfPackages <- c("tidyverse", "tidyr","devtools","RColorBrewer", "knitr", "kableExtra", "tsModel", "gridExtra", "dplyr", "metafor", "meta", "viridis", "UpSetR", "scales", "EHRtemporalVariability")
paket(listOfPackages)

@@

perc_disorder_group_total %>%
  ggplot( aes( x= as.Date( time_p ), y = percentage, group = disorder_group )) +
  facet_wrap( ~ disorder_group, scales = "free" ) +
  geom_line( aes(color = disorder_group )) +
  geom_point( aes( color = disorder_group )) +
  geom_vline(xintercept = as.Date(pandemic_start_date), linetype = "dashed")+
  labs(x ="", y = "percentage of patients (%)")+
  scale_x_date(breaks = "1 month", labels=date_format("%b-%y"), expand=c(0.03,0))+
  theme(axis.text.x=element_text(angle = 45, hjust=1, size = 6),
        panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        panel.border = element_rect(colour = "black", fill = NA))

percentages_htm <- perc_disorder_group_total %>%
  select( time_p, disorder_group, percentage ) %>%
  unique() %>%
  pivot_wider( names_from =  disorder_group, 
               values_from = percentage )

dates <- percentages_htm$time_p

percentages_htm <- percentages_htm[  , -1]

counts_htm <- perc_disorder_group_total %>%
  select( time_p, disorder_group, dg_cases ) %>%
  unique() %>%
  pivot_wider( names_from =  disorder_group, 
               values_from = dg_cases )
counts_htm <- counts_htm[  , -1]

tempVariabilityInput <- new('DataTemporalMap', probabilityMap = as.matrix(percentages_htm), 
         countsMap = as.matrix(counts_htm), dates = dates, support = as.data.frame(names(percentages_htm)), 
         variableName = "example", variableType = "character", period = "month")
plotDataTemporalMap(tempVariabilityInput, absolute = TRUE)

#### facet wrap in 3 groups based on %
### most prevalent
perc_disorder_group_total %>%
  filter(disorder_group %in% c("Anxiety Disorders", "Depressive Disorders", "Suicide or Self-Injury" ))  %>%
  ggplot( aes( x= as.Date( time_p ), y = percentage, group = country )) +
  facet_wrap( ~ disorder_group ) +
  geom_line( aes(color = country )) +
  geom_point( aes( color = country )) +
  geom_vline(xintercept = as.Date(pandemic_start_date), linetype = "dashed")+
  labs(x ="", y = "percentage of patients (%)")+
  scale_x_date(breaks = "1 month", labels=date_format("%b-%y"), expand=c(0.03,0))+
  theme(axis.text.x=element_text(angle = 45, hjust=1, size = 6),
        panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        panel.border = element_rect(colour = "black", fill = NA)) +
  scale_color_manual( values = cbPalette )

#medium prevalent
perc_disorder_group_total %>%
  filter(disorder_group %in% c("Trauma and Stressor-Related Disorders", "Mental Health Symptom", "Disruptive, Impulse Control and Conduct Disorders", 
                               "Feeding and Eating Disorders"))  %>%
  ggplot( aes( x= as.Date( time_p ), y = percentage, group = country )) +
  facet_wrap( ~ disorder_group ) +
  geom_line( aes(color = country )) +
  geom_point( aes( color = country )) +
  geom_vline(xintercept = as.Date(pandemic_start_date), linetype = "dashed")+
  labs(x ="", y = "percentage of patients (%)")+
  scale_x_date(breaks = "1 month", labels=date_format("%b-%y"), expand=c(0.03,0))+
  theme(axis.text.x=element_text(angle = 45, hjust=1, size = 6),
        panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        panel.border = element_rect(colour = "black", fill = NA)) +
  scale_color_manual( values = cbPalette )

#low prevalent
perc_disorder_group_total %>%
  filter(disorder_group %in% c("Miscellaneous", "Substance-Related and Addictive Disorders", 
                               "Personality Disorders", "Bipolar and Related Disorders", "Sleep-Wake Disorders", 
                               "Schizophrenia Spectrum and Other Psychotic Disorders", "Somatic Symptom and Related Disorders", 
                               "Obsessive-Compulsive and Related Disorders", "Dissociative Disorders" ))  %>%
  ggplot( aes( x= as.Date( time_p ), y = percentage, group = country )) +
  facet_wrap( ~ disorder_group ) +
  geom_line( aes(color = country )) +
  geom_point( aes( color = country )) +
  geom_vline(xintercept = as.Date(pandemic_start_date), linetype = "dashed")+
  labs(x ="", y = "percentage of patients (%)")+
  scale_x_date(breaks = "1 month", labels=date_format("%b-%y"), expand=c(0.03,0))+
  theme(axis.text.x=element_text(angle = 45, hjust=1, size = 6),
        panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        panel.border = element_rect(colour = "black", fill = NA)) +
  scale_color_manual( values = cbPalette )

perc_disorder_group_total %>%
  filter(disorder_group %in% c("Anxiety Disorders", "Depressive Disorders", "Suicide or Self-Injury" ))  %>%
  ggplot( aes( x= as.Date( time_p ), y = percentage, group = country )) +
  facet_wrap( ~ disorder_group ) +
  geom_line( aes(color = country )) +
  geom_point( aes( color = country )) +
  geom_vline(xintercept = as.Date(pandemic_start_date), linetype = "dashed") +
  labs(x ="", y = "percentage of patients (%)")+
  scale_x_date(breaks = "1 month", labels=date_format("%b-%y"), expand=c(0.03,0)) +
  scale_color_manual( values = cbPalette ) + 
  theme(axis.text.x=element_text(angle = 45, hjust=1, size = 6), 
        strip.text = element_text(size = 10, face = "bold"),
        panel.grid.major = element_blank(), panel.grid.minor = element_blank(), strip.background = element_blank(),
        panel.border = element_rect(colour = "black", fill = NA), 
        legend.position="bottom")
